### 2015-01-15 src/analysis.Rnw
results
update

\begin{table*}[!ht]
\caption*{Selective}
<<results='asis'>>=
print(xtable(s.selective.db, caption='Selective', label='table:selective'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The operator selection criteria results. }
\label{tbl:lcountl}
\end{table*}

\begin{table*}[!ht]
\caption*{N-Selection}
<<results='asis'>>=
print(xtable(s.nselection.db, caption='N-Selection', label='table:nselection'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The n-selection criteria results}
\label{tbl:lcountl}
\end{table*}

\begin{table*}[!ht]
\caption*{Single Operators}
<<results='asis'>>=
print(xtable(s.singles.db, caption='Single Operators', label='table:singles'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The single operator selection results}
\label{tbl:lcountl}
\end{table*}

\begin{table*}[!ht]
\caption*{Operator Samples x\%}
<<results='asis'>>=
print(xtable(s.opsample.db, caption='Operator x samples', label='table:opsample'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The operator x\% sample criteria results}
\label{tbl:lcountl}
\end{table*}

\begin{table*}[!ht]
\caption*{Element Scoped}
<<results='asis'>>=
print(xtable(s.lmcp.db, caption='Element Scoped', label='table:element'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The element based sampling criteria results. }
\label{tbl:lcountl}
\end{table*}

>>>>

\begin{table*}[!ht]
%\caption*{Selective}
<<results='asis'>>=
tbl.place <- function(xtb) {
  align(xtb) <- "p{0.1\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}|p{0.15\\textwidth}"
  return(xtb)
}
print(tbl.place(xtable(s.selective.db, caption='Selective Strategy', label='table:selective')),include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The operator selection strategy}
\label{tbl:selective}
\end{table*}

\begin{table*}[!ht]
%\caption*{N-Selection}
<<results='asis'>>=
print(tbl.place(xtable(s.nselection.db, caption='N-Selection', label='table:nselection')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The N-selective strategy}
\label{tbl:nselection}
\end{table*}

\begin{table*}[!ht]
%\caption*{Operator Samples x\%}
<<results='asis'>>=
print(tbl.place(xtable(s.opsample.db, caption='Operator x samples', label='table:opsample')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The operator based fractional sample strategy}
\label{tbl:opsample}
\end{table*}

\begin{table*}[!ht]
%\caption*{Element Scoped}
<<results='asis'>>=
print(tbl.place(xtable(s.lmcp.db, caption='Element Scoped', label='table:element')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The element based fractional sample strategy}
\label{tbl:element}
\end{table*}

\begin{table*}[!ht]
%\caption*{Single Operators}
<<results='asis'>>=
print(tbl.place(xtable(s.singles.db, caption='Single Operators', label='table:singles')), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The single operator selection strategy}
\label{tbl:singles}
\end{table*}
